A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Figures

### 2019-09-05 writeUp/supplementary_materials.tex
Updated POA and SOM

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_gonotrophicCycleRaw.pdf}}
	\caption{\textbf{Raw gonotrophic cycle duration estimates for A. the 1st cycle and B. subsequent cycles.} The confidence intervals represent a range of uncertainties since they were not available in a standardised form (see Section \ref{sec:dissection_gonotrophicMethod} for a discussion of how we handle this issue). If no statement of uncertainty was given in the estimates then we indicate this by a triangle marker. The studies are ordered according to the central estimate of gonotrophic duration.}\label{fig:dissection_gonotrophicCycleRaw}
\end{figure}

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_gonotrophicCycleRaw_MRRVsLab.pdf}}
	\caption{\textbf{Raw gonotrophic cycle duration estimates from A. the MRR and B. from laboratory-based studies.} The confidence intervals represent heterogeneous measures since they were not available in a standardised form (see Section \ref{sec:dissection_gonotrophicMethod} for a discussion of we handle this issue). If no statement of uncertainty was given in the estimates then we indicate this by a triangle marker. The studies are ordered according to the central estimate of gonotrophic duration.}\label{fig:dissection_gonotrophicCycleRaw_MRRVsLab}
\end{figure}

>>>>

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/gonotrophic_data.pdf}}
	\caption{\textbf{Raw gonotrophic cycle duration estimates for A. the 1st cycle and B. subsequent cycles.} When present, the confidence intervals represent our estimates of the 95\% confidence interval on gonotrophic cycle duration (see Section \ref{sec:dissection_gonotrophicMethod} for a discussion of how we handle this issue); if our estimate of the lower limit was below zero, we deemed this unbiological and set it to 1 day for this graph. If no statement of uncertainty was given in the estimates then we indicate this by a triangle marker. The studies are ordered within each Genus according to the central estimate of gonotrophic duration.}\label{fig:dissection_gonotrophicCycleRaw}
\end{figure}
